I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-04-27 lipics-master/comppaths.tex
also changed in 4.3 sketch of TH5

We cannot define the Sign function on nodes from which a compensating path can be reached.
However, we can define the sign function for neurons in $A_{pure}$ and $B_{pure}$.
Further, the set of nodes on which the sign function is defined is suffix-closed:

>>>>

We cannot define the influence sign function $S$ on nodes from which a compensating path can be reached. However, we can define $S(n)$ for neurons $n$ in $A_{pure}$ and $B_{pure}$.
Further, the set of nodes $n$ on which the $S(n)$ is defined is suffix-closed:
